%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
% \usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean
% Uncomment to enable Chinese; needs XeLaTeX
\usepackage{ctex}


% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{刘健恒}{}
%\title{Curriculum Vitae}                               % optional, remove / comment the line if not wanted
%\address{Sanchez de Bustamante, 731, Buenos Aires, Argentina}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+86 15625293598}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{01234 123456}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{943678231@qq.com}                               % optional, remove / comment the line if not wanted
\homepage{https://github.com/jianhengLiu}                         % optional, remove / comment the line if not wanted  
\extrainfo{https://jianhengliu.github.io/}                 % optional, remove / comment the line if not wanted
% \photo[64pt][0.4pt]{potrait.jpeg}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\small{我目前的研究兴趣聚焦于\textbf{机器人的感知定位与运动规划}，现于\href{faculty.hitsz.edu.cn/chenhaoyao}{陈浩耀}教授带领的\href{http://nrs-lab.com/}{nROS-Lab(NRSL)})攻读学术型研究生学位。

\section{Education}

\vspace{5pt}

\begin{itemize}

\item{\cventry{2021/09--Present}{控制科学与工程 (研究生学位)}{哈尔滨工业大学（深圳）}{推免生}{\textit{}}{}}

\item{\cventry{2017/09--2021/06}{自动化 (学士学位)}{哈尔滨工业大学（深圳）}{15/70}{\textit{}}{}}

\end{itemize}

\vspace{2pt}

\section{Publication}

\vspace{5pt}

\begin{itemize}
    

\item{\textbf{RGB-D Inertial Odometry for a Resource-restricted Robot in Dynamic Environments}

\small{\textbf{Jianheng Liu}, XuanFu Li, Yueqian Liu and Haoyao Chen}
% \small{\textbf{Jianheng Liu}*, Yunfan Ren*, Haoyao Chen and Yunhui Liu}

\small{RA-L and IROS, 2022 (\textbf{Under review}) }
}

\vspace{3pt}

\item{\textbf{Vision-encoder-based Payload State Estimation for Autonomous MAV With a Suspended Payload}

\small{\textbf{Jianheng Liu}, Yunfan Ren, Haoyao Chen and Yunhui Liu}
% \small{\textbf{Jianheng Liu}*, Yunfan Ren*, Haoyao Chen and Yunhui Liu}

\small{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS, 2021) }
}

% \small{* co-first author}

\end{itemize}

\section{Honor \& Awards}

\vspace{6pt}

\begin{itemize}

\item{Graduate Academic Scholarship of First-class (2021-2022), Undergraduate Academic Scholarship of First-class (2019-2020), Third-class (2018-2019), Second-class (2017-2018)}

\item{National ROBOCON competition of First Price (2020), Second Price (2019)}

\item{the Third Prize for 2019 National Challenge Cup, the Bronze Prize for 2019 Internet plus of Heilongjiang Province, the Golden Price for 2019  ZuGuang Cup of Harbin Institute of Technology (Shenzhen)}

\item{the Second Prize for 2018 National English Competition for College Strudents}

\item{the Grand Prize for the second International Youth Drone Competition}

\end{itemize}


\section{Research}

\vspace{6pt}

\begin{itemize}

\item \textbf{RGB-D Inertial Odometry for a Resource-restricted Robot in Dynamic Environments:} 

\textbf{Jianheng Liu}, XuanFu Li, Yueqian Liu and Haoyao Chen

RA-L and IROS, 2022 (\textbf{Under review})

We develops a novel real-time system for estimating the payload position; the system consists of a monocular fisheye camera and a novel encoder-based device. A Gaussian fusion-based estimation algorithm is developed to obtain the payload state estimation. Based on the robust payload position estimation, a payload controller is presented to ensure the reliable tracking performance on aggressive trajectories. Several experiments are performed to validate the high performance of the proposed method. 

\begin{itemize}
\item \textbf{Referred Code:} \href{https://github.com/jianhengLiu/Vision-encoder-based-Payload-State-Estimator}{Code}
\item \textbf{Referred Video:} \href{https://www.bilibili.com/video/BV1Qq4y1U7n4?share_source=copy_web}{Video}
\end{itemize}
\vspace{6pt}

\item \textbf{Dynamic-VINS:} Dynamic-VINS is a SLAM system based on VINS-RGBD-FAST. I try to combine YOLOv3 to eliminate the impact of the dynamic feature to SLAM system. The whole system is conducted in HUAWEI Atlas 200DK. A resposity adapting YOLOv3 and ROS to Atlas200DK is released to \href{https://github.com/jianhengLiu/YOLOv3-Atlas-ROS}{\textbf{YOLOv3-Atlas-ROS}}.

\vspace{6pt}

\item \textbf{VINS-RGBD-FAST:} VINS-RGBD-FAST is a SLAM system based on VINS-RGBD. I do some refinements both in frontend and backend to improve the system's efficiency in resource-constrained embedded paltform, like HUAWEI Atlas 200DK, Raspberry Pi. For example, this system extracts FAST feature instead of Harris feature and solved feature clusttering problem, adds stationary initialization function, add IMU-aided feature tracking and extracted-feature area's quality judgement function, lowers the required bandwidth of the system, makes a trade-off of accuracy and efficiency by constrain the optimized variables in backend. Furthermore, we made this system as a module and applied it into UAV as a state feedback to track a generative trajectory stably. 

\begin{itemize}
\item \textbf{Referred Code:} \href{https://github.com/jianhengLiu/VINS-RGBD-FAST}{Code}.
\end{itemize}
\vspace{6pt}
\vspace{6pt}

\item \textbf{Vision-encoder-based Payload State Estimation for Autonomous MAV With a Suspended Payload:} 

\textbf{Jianheng Liu}*, Yunfan Ren*, Haoyao Chen and Yunhui Liu

IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS, 2021)

We develops a novel real-time system for estimating the payload position; the system consists of a monocular fisheye camera and a novel encoder-based device. A Gaussian fusion-based estimation algorithm is developed to obtain the payload state estimation. Based on the robust payload position estimation, a payload controller is presented to ensure the reliable tracking performance on aggressive trajectories. Several experiments are performed to validate the high performance of the proposed method. 

\begin{itemize}
\item \textbf{Referred Code:} \href{https://github.com/jianhengLiu/Vision-encoder-based-Payload-State-Estimator}{Code}
\item \textbf{Referred Video:} \href{https://www.bilibili.com/video/BV1Qq4y1U7n4?share_source=copy_web}{Video}
\end{itemize}
\vspace{6pt}

\item \textbf{MatRix:} A extreme interesting prototype developed in 2020 XBOT PARK Smart Product Innovation Boot Camp. An interactive smart carpet, which can achieve infinite splicing through the magnetic suction connector with anti-dull design. MatRix can be used as your home intelligent terminal, game console, decoration and so on.

\begin{itemize}
\item \textbf{Referred Video:} \href{https://www.bilibili.com/video/BV1gb4y127by?share_source=copy_web}{Video}
\end{itemize}

\vspace{6pt}

\item \textbf{quad-controller-SE3 \& FlightController:} quadrotor controller based on PX4/mavros and SE3 geometric control. And I also develop a simulation based on CoppeliaSim software to compute the desired thrust and torque of quadroter according to dynamic modelling, and use distribution matrix to decide the motor's speed. Furthermore, I conduct a trajectory tracking controller to follow a generative minimum snap trajectory for experiment.

\begin{itemize}
\item \textbf{Referred Code:} \href{https://github.com/jianhengLiu/quad_controller_SE3}{quad-controller-SE3}, \href{https://github.com/jianhengLiu/FlightController}{FlightController}

\item \textbf{Referred Video:} \href{https://www.bilibili.com/video/BV1xv411w7Md?share_source=copy_web}{Video1}, \href{https://www.bilibili.com/video/BV1rq4y1N76T?share_source=copy_web}{Video2}
\end{itemize}

\vspace{6pt}

\item \textbf{BezierTrajGenerator \& MinimumSnapTrajGenerator \& 
MapManager:} Trajectory Generator based on Bezier Curve and Minimum Snap for autonomous robot. And I develop a 2D Map Manager for the verification and visualization for different algorithms.

\begin{itemize}
\item \textbf{Referred Code:} \href{https://github.com/jianhengLiu/BezierTrajGenerator}{BezierTrajGenerator}, \href{https://github.com/jianhengLiu/MinimumSnapTrajGenerator}{MinimumSnapTrajGenerator}, \href{https://github.com/jianhengLiu/MapManager}{MapManager}
\end{itemize}

\vspace{6pt}

\item \textbf{CoppeliaSim/V-Rep Steeling Wheel Robot Tutorial:} A detailed tutorial for a CoppeliaSim/V-Rep beginner to construct their own Steeling Wheel Robot and control it via ROS.

\begin{itemize}
\item \textbf{Referred Code:} \href{https://github.com/jianhengLiu/CoppeliaSim_Steeringwheel_Tutorial}{CoppeliaSim-Steeringwheel-Tutorial}
\end{itemize}
\vspace{6pt}

\item \textbf{Manipulator-GUI:} C++ Course Project (Complied in CodeBlocks). A three dimentional manipulator's forword/inverse kinematics calculation and visualization.

\begin{itemize}
\item \textbf{Referred Code:} \href{https://github.com/jianhengLiu/Manipulator_GUI}{Manipulator-GUI}
\end{itemize}

\end{itemize}


% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------

\end{document}


%% end of file `template.tex'.
